Numerical trajectory patterns of floating macroalgae

### 2020-11-02 thesis_chapter_3.Rmd
changed and updated simulation table

sim_table <- flextable(data = sim_table)
sim_table <- theme_zebra(sim_table, odd_header = "transparent", even_header = "transparent")
sim_table <- set_header_labels(sim_table, Particle.behaviour = "Particle behaviour", Cross.sectional.area = "Cross-sectional area", Time.Range = "Time Range", Release.Lon = "Release longitude", Release.Lat = "Release Latitude", Hydrodynamic.model = "Hydrodynamic model", Wind.Model = "Wind model")
sim_table <- align(x= sim_table, align = "center", part = "all")
sim_table

@@

>>>>

@@

sim_table <- flextable(data = sim_table)
sim_table <- theme_zebra(sim_table, odd_header = "transparent", even_header = "transparent")
sim_table <- set_header_labels(sim_table, Cross.sectional.area = "Cross-sectional area", Time.Range = "Time Range", Drag.Exposure = "Drag Exposure level")
sim_table <- align(x= sim_table, align = "center", part = "all")
sim_table
